Supporting Information for\\ ``A weakly structured stem for human origins in Africa''

### 2022-01-07 supplement.tex
some captions

\subsection{$f_4$ statistics between pairs of contemporary and pairs of ancient populations}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/supp-h12s-all-models.pdf}
    \caption{
        \textbf{Predicted pairwise differentiation between contemporaneous populations.}
        \aprcomment{Plot ordering, line colors and styles, etc need to be cleaned up.
        Add panel labels.}
        All models (A: single origin, B: continuous migration, C: merger without stem
        migration, D: merger with stem migration)\dots
    }
    \label{fig:supp-h12-panels}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-single-origin.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of modern populations
        and ancient branches from the single-origin model.}
    }
    \label{fig:supp-f4s-single-origin}
\end{figure}

>>>>

\subsection{$f_4$ statistics between pairs of contemporary and pairs of ancient populations}
\label{sec:f4}

@@

\begin{figure}[ht]
    \centering
    \includegraphics[width=\textwidth]{figures/supp-h12s-all-models.pdf}
    \caption{
        \textbf{Predicted pairwise differentiation between contemporaneous populations.}
        \aprcomment{Plot ordering, line colors and styles, etc need to be cleaned up.
        Add panel labels.}
        $H_{i,j}$ is the predicted pairwise differentiaion between two populations,
        which we normalize by the observed pairwise diversity in the Mende sample.
        The single-origin model (A) shows larger deviations between observed and
        expected differentiation than the models with early human structure
        (B: continuousmigration, C: merger without stem migration, D: merger with 
        stem migration). In the merger models (C and D), while $F_{ST}$ is large
        between early stems due to the sharp bottleneck in one of those branches,
        the pairwise differences are comparable to the continuous-migration model.
        Stem 1E and Stem 1S have low differentiation, as the bottleneck in Stem 1
        (which they both split from) sharply reduces diversity by the time of the
        split. This has the effect of large $F_{ST}$ but small $H_{i,j}$.
    }
    \label{fig:supp-h12-panels}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics{figures/supp-f4s-single-origin.pdf}
    \caption{
        \textbf{Predicted \bm{$f_4$} between pairs of modern populations
        and ancient branches from the single-origin model.}
        $f_4(A, B; X, Y)/f_2(A, B)f_2(X, Y)$ is interpreted as the proportion of the
        amount of drift between sampled populations $A$ and $B$ that can be
        attributed to drift between populations $X$ and $Y$, sampled in the past
        (see Section~\ref{sec:f4}). \aprcomment{\dots}
    }
    \label{fig:supp-f4s-single-origin}
\end{figure}
